Introduction of using AWS instance to run experiments

### 2022-03-20 docs/run_experiments.Rmd
Add new loss and modify some details

Hum... Using a bigger weight for cropland in loss calculation increased the accuracy significantly.

@@

Zone 1, 2, 3, 4, 5
```
python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 121
```

@@

@@

```
while true; do aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1; sleep 50m; done
```

```
aws s3 cp --recursive s3://activemapper/leisong/unet_z1245_12bs_4augs_ft_80epochs/ $HOME/hrlcm/results/dl/unet_z1245_12bs_4augs_ft_80epochs
```

>>>>

Hum... Using a bigger weight for cropland in loss calculation increased the overall accuracy a bit. However, the cost is the overestimation of cropland over sparse vegetation area.

@@

Zone 1, 2, 3, 4, 5
```
python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_ew_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 121
```

@@

#### "Hierarchical" training with dynamic loss function

First, train a general model with relatively large learning rate (0.001 - 0.0001), balanced cross entropy loss function, and full training dataset for 80 epochs:

```
python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0001 --max_lr 0.001 --save_freq 20 --epochs 81
```

Then, transfer with updating weights of all layers. It uses relatively small learning rate (0.0001 - 0.000001) with a dynamic loss that is a weighted average of BCE and Lovász-Softmax.

Take zone1 as an example:

```
python hrlcm/fit_compose_lr.py --exp_name unet_z1_12bs_4augs_ft_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.000001 --max_lr 0.0001 --save_freq 20 --epochs 121 --resume 'results/dl/unet_full_12bs_4augs_80epochs/checkpoints/final.pth'
```

@@

```
while true; do aws s3 cp --recursive $HOME/hrlcm/results/prediction_zone1 s3://activemapper/leisong/prediction/zone1_only; sleep 50m; done
```

```
aws s3 cp --recursive s3://activemapper/leisong/unet_full_12bs_4augs_120epochs/ $HOME/hrlcm/results/dl/unet_full_12bs_4augs_120epochs
```
